---
title: "Model Update"
output: html_document
date: "2024-04-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyr)
library(ggplot2)
library(plotly)
library(knitr)
library(viridisLite)
library(readxl)
library(zoo)
library(stringr)
library(ggpubr)

```

```{r data, include=FALSE}
# load main data frame to be used

# # 1. for comparison of shapes of waning and aging
# one <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/prefitting/prefitted_model_scot.rds")
# two <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/prefitting/prefitted_model_linear.rds")
# three <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/prefitting/prefitted_model_exponential.rds")
# 
# # 2. for comparison of rates
# one <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/prefitting/prefitted_model.rds")
# two <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/prefitting/prefitted_model_mobility.rds")
# three <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/prefitting/prefitted_model_scot.rds")

# 3. for comparison of probabilities
one <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/prefitting/prefitted_model_functionised.rds")
two <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/prefitting/prefitted_model_functionised_linear.rds")
three <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/prefitting/prefitted_model_functionised_exponential.rds")

# load other datasets

# load mobility data
mobility <- read.csv(file = "/Users/lsh2301561/Desktop/rsv_disruption/data/changes-visitors-covid.csv") %>%
  filter(Code == "GBR") %>%
  mutate(Day = as.Date(Day, format = "%Y-%m-%d")) %>%
  pivot_longer(cols = `retail_and_recreation`:`workplaces`, names_to = "category", values_to = "value")

# load birth data
birth_data <- read_excel("/Users/lsh2301561/Desktop/rsv_disruption/data/births-time-series-22-bt.3.xlsx", skip = 3) %>% 
  head(-7) %>% 
  select(1:14) %>% 
  select(-Total) %>% 
  rename(year = Year) %>% 
  pivot_longer(cols = `Jan`:`Dec`, names_to = "month", values_to = "births") %>% 
  filter(year >= 2012, year <= 2021) %>% 
  mutate(month = rep(month.abb, 10),
         year_month = paste(year, month, sep = "_"),
         date = as.Date(as.yearmon(`year_month`, "%Y_%b"))) %>%
  select(year, month, date, births) %>% 
  mutate(time = 1:nrow(.))

# # create reference table for rates to join
# rate_reference <- readRDS("/Users/lsh2301561/Desktop/rsv_disruption/output/data/women/women_rate_prefitting_scot.rds") %>% 
#   select(time, month, rate) %>% 
#   distinct() %>% 
#   filter(time <= 12*75, time > 12*60) %>% 
#   mutate(month = factor(month, levels = month.abb),
#          time = 1:nrow(.)) %>% 
#   cross_join(data.frame(level = 1:4)) %>% 
#   mutate(level = factor(level, levels = 1:4))

# # create 10 years of infection history/immunity split
# immunity_split <- readRDS("/Users/lsh2301561/Desktop/rsv_disruption/output/data/women/women_rate_prefitting_scot.rds") %>%
#   filter(time <= 12*70, time > 12*60) %>%
#   mutate(month = factor(month, levels = month.abb)) %>%
#   filter(infection != "susceptible_naive") %>%
#   mutate(level = as.factor(case_when(infection %in% str_c(rep("I", 6), 1:6) ~ 1,
#                                      infection %in% str_c(rep("I", 9), 7:15) ~ 2,
#                                      infection %in% str_c(rep("I", 9), 16:24) ~ 3,
#                                      infection == "susceptible_reinf" ~ 4))) %>%
#   group_by(time, rate, month, level) %>%
#   summarise(across(c("count", "proportion"), sum, na.rm = TRUE)) %>%
#   ungroup() %>%
#   mutate(time = rep(1:(12*10), each = 4)) %>%
#   # combining with birth data
#   select(-count) %>%
#   left_join(birth_data %>% select(month, births, time)) %>%
#   mutate(susceptible = proportion * births)

# scottish population data by age
population <- read_excel("/Users/lsh2301561/Desktop/rsv_disruption/data/mid-year-pop-est-22-data.xlsx", sheet = "Table 1", skip = 3) %>% 
  filter(`Area name` == "Scotland",
         Sex == "Persons") %>% 
  select(1:10) %>% 
  select(-`All ages`) %>% 
  pivot_longer(cols = `0`:`4`, names_to = "age_year", values_to = "population") %>% 
  mutate(age = ifelse(age_year == 0, "<1", "1-4")) %>% 
  group_by(age) %>% 
  summarise(population = sum(population))

```

```{r plot, include=FALSE}
# shapes object for lockdown period in plots
lockdown <- list(list(type = "line",
                            y0 = 0,
                            y1 = 1,
                            yref = "paper",
                            x0 = 12*5+3,
                            x1 = 12*5+3,
                            line = list(color = "red", dash="dot")),
                       list(type = "line",
                            y0 = 0,
                            y1 = 1,
                            yref = "paper",
                            x0 = 12*6+3,
                            x1 = 12*6+3,
                            line = list(color = "red", dash="dot")),
                       list(type = "rect",
                            xref = "x",
                            yref = "paper",
                            x0 = 63,
                            y0 = 0,
                            x1 = 66,
                            y1 = 1,
                            fillcolor = "red",
                            opacity = 0.8,
                            line = list(width = 0)),
                       list(type = "rect",
                            xref = "x",
                            yref = "paper",
                            x0 = 66,
                            y0 = 0,
                            x1 = 67,
                            y1 = 1,
                            fillcolor = "red",
                            opacity = 0.6,
                            line = list(width = 0)),
                       list(type = "rect",
                            xref = "x",
                            yref = "paper",
                            x0 = 67,
                            y0 = 0,
                            x1 = 68,
                            y1 = 1,
                            fillcolor = "red",
                            opacity = 0.4,
                            line = list(width = 0)),
                       list(type = "rect",
                            xref = "x",
                            yref = "paper",
                            x0 = 68,
                            y0 = 0,
                            x1 = 69,
                            y1 = 1,
                            fillcolor = "red",
                            opacity = 0.2,
                            line = list(width = 0)),
                       list(type = "rect",
                            xref = "x",
                            yref = "paper",
                            x0 = 69,
                            y0 = 0,
                            x1 = 70,
                            y1 = 1,
                            fillcolor = "red",
                            opacity = 0.4,
                            line = list(width = 0)),
                       list(type = "rect",
                            xref = "x",
                            yref = "paper",
                            x0 = 70,
                            y0 = 0,
                            x1 = 71,
                            y1 = 1,
                            fillcolor = "red",
                            opacity = 0.6,
                            line = list(width = 0)),
                       list(type = "rect",
                            xref = "x",
                            yref = "paper",
                            x0 = 71,
                            y0 = 0,
                            x1 = 72,
                            y1 = 1,
                            fillcolor = "red",
                            opacity = 0.8,
                            line = list(width = 0)),
                       list(type = "rect",
                            xref = "x",
                            yref = "paper",
                            x0 = 72,
                            y0 = 0,
                            x1 = 73,
                            y1 = 1,
                            fillcolor = "red",
                            opacity = 0.4,
                            line = list(width = 0)),
                        list(type = "rect",
                            xref = "x",
                            yref = "paper",
                            x0 = 73,
                            y0 = 0,
                            x1 = 76,
                            y1 = 1,
                            fillcolor = "red",
                            opacity = 0.8,
                            line = list(width = 0)),
                        list(type = "rect",
                            xref = "x",
                            yref = "paper",
                            x0 = 76,
                            y0 = 0,
                            x1 = 79,
                            y1 = 1,
                            fillcolor = "red",
                            opacity = 0.4,
                            line = list(width = 0)))

# plotting function for infection and disease curve
plot_curve <- function(data, max = c(), tick =c(), ind = c("infected", "disease")){
  data %>%
  group_by(time_calendar, month, rate) %>%
  summarise(across(c("susceptible", "infected", "disease"), sum, na.rm = TRUE)) %>%
  ungroup() %>%
  pivot_longer(cols = c("susceptible", "infected", "disease"), names_to = "type", values_to = "count") %>%
  filter(type == ind) %>%
  plot_ly() %>%
  add_trace(
    x = ~time_calendar,
    y = ~count,
    type = "scatter",
    mode = "line",
    text = ~month
  ) %>%
  # add_trace(data = mobility,
  #       x = ~time_calendar,
  #       y = ~value,
  #       split = ~category,
  #       group = "Mobility",
  #       colour = ~category,
  #       type = 'scatter',
  #       mode = 'lines',
  #       yaxis = "y2") %>%
  layout(xaxis = list(title = "Calendar month",
                      range = list(37, 120),
                      tickvals = seq(37, 120, 3),
                      ticktext = rep(c("Jan", "Apr", "Jul", "Oct"), 7),
                      tickmode = "array",
                      tickangle = -45),
         yaxis = list(title = "Count",
                      range = list(0, max),
                      tickmode = "linear",
                      tick0 = 0,
                      dtick = tick,
                      tickformat = "digits",
                      side = "left"),
         # yaxis2 = list(
         #   overlaying = "y",
         #   side = "right",
         #   title = "Change in Mobility"),
         shapes = lockdown)
}

plot_split <- function(data, max = c(), tick =c(), ind = c("infected", "disease")){
  data %>% 
  group_by(time_calendar, month, rate, level) %>% 
  summarise(across(c("susceptible", "infected", "disease"), sum, na.rm = TRUE)) %>% 
  ungroup() %>% 
    pivot_longer(cols = c("susceptible", "infected", "disease"), names_to = "type", values_to = "count") %>%
  filter(type == ind) %>% 
  plot_ly() %>% 
  add_trace(
    x = ~time_calendar,
    y = ~count,
    type = "scatter",
    mode = "line",
    split = ~level,
    color = ~level, 
    # colors = c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728"),
    text = ~month,
    hovertemplate = paste('<b>Month</b>: %{text}',
                          '<br><b>Count</b>: %{y}',
                          '<extra></extra>')
  ) %>% 
  layout(xaxis = list(title = "Calendar month",
                      range = list(37, 120),
                      tickvals = seq(37, 120, 3),
                      ticktext = rep(c("Jan", "Apr", "Jul", "Oct"), 7),
                      tickmode = "array",
                      tickangle = -45),
         yaxis = list(title = "Infection Count",
                      range = list(0, max),
                      tickmode = "linear",
                      tick0 = 0,
                      dtick = tick, 
                      tickformat = "digits"),
         legend = list(title = list(text = "Immunity Level")),
         shapes = lockdown)
}

plot_bar <- function(data, ind = c("infected", "disease")){
  data %>% 
  select(-time) %>% 
  pivot_longer(cols = c("<6", "6-12", "12-24", "24-36"), names_to = "age", values_to = "value") %>%
  mutate(age = factor(age, levels = c("<6", "6-12", "12-24", "24-36"))) %>% 
  filter(value == 1) %>% 
  select(-value) %>% 
  group_by(time_calendar, month, rate, age) %>% 
  summarise(infected = sum(infected),
            disease = sum(disease)) %>% 
  ungroup() %>% 
  pivot_longer(cols = c("infected", "disease"), names_to = "type", values_to = "count") %>% 
  left_join(data %>%
            group_by(time_calendar, month, rate) %>%
            summarise(across(c("infected", "disease"), sum, na.rm = TRUE)) %>%
            ungroup() %>%
            pivot_longer(cols = c("infected", "disease"), names_to = "type", values_to = "sum")) %>%
  mutate(proportion = (count/sum)*100) %>% 
  filter(type == ind) %>% 
  plot_ly() %>%
  add_trace(x = ~time_calendar,
            y = ~proportion,
            split = ~age,
            color = ~age, 
            colors = c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728"),
            legendgroup = ~age,
            type = "bar",
            showlegend = TRUE) %>% 
  layout(xaxis = list(title = "Calendar Month",
                      range = list(37, 120),
                      tickvals = seq(37, 120, 3),
                      ticktext = rep(c("Jan", "Apr", "Jul", "Oct"), 7),
                      tickmode = "array",
                      tickangle = -45),
         yaxis = list(title = "Proportion"),
         legend = list(title = list(text = "Age Group")),
         barmode = "stack",
         shapes = lockdown)
}

plot_rate <- function(data, max = c(), tick =c(), ind = c("infected", "disease")){
  data %>% 
  select(-time) %>% 
  mutate(age = case_when(time_birth  < 12 ~ "<1",
                         time_birth >= 12 & time_birth  <= 48 ~ "1-4")) %>%
  group_by(time_calendar, month, rate, age) %>% 
  summarise(infected = sum(infected),
            disease = sum(disease)) %>% 
  ungroup() %>% 
  pivot_longer(cols = c("infected", "disease"), names_to = "type", values_to = "count") %>%
  left_join(population) %>% 
  mutate(rate = (count/population)*100000) %>% 
  # visualise
  filter(type == ind) %>% 
  plot_ly() %>%
  add_trace(
    x = ~time_calendar,
    y = ~rate,
    split = ~age,
    colour = ~age,
    type = "scatter",
    mode = "line",
    text = ~month
  ) %>%
  layout(xaxis = list(title = "Calendar month",
                      range = list(37, 120),
                      tickvals = seq(37, 120, 3),
                      ticktext = rep(c("Jan", "Apr", "Jul", "Oct"), 7),
                      tickmode = "array",
                      tickangle = -45),
         yaxis = list(title = "Rate (per 100,000)",
                      range = list(0, max),
                      tickmode = "linear",
                      tick0 = 0,
                      dtick = tick,
                      tickformat = "digits",
                      side = "left"),
         shapes = lockdown)
}

```

# Immunity

**infection history in mothers**
```{r women_prop_rate, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot infection history proportions
ggpubr::ggarrange(readRDS("/Users/lsh2301561/Desktop/rsv_disruption/output/data/women/women_rate_prefitting.rds") %>%
                    filter(time <= 12*70, time > 12*60) %>%
                    ggplot() +
                    geom_bar(aes(x = time, y = proportion, fill = infection), position = "fill", stat = "identity") +
                    scale_fill_manual(values = c("lightgrey", "darkgrey", viridis(24))) +
                    scale_x_continuous(breaks = seq(1, 901, 6), labels = c(rep(c("January", "July"), 75), "January")) +
                    theme_bw() +
                    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                    labs(x = "Time",
                         y = "Proportion",
                         fill = "Infection Status"),
                  readRDS("/Users/lsh2301561/Desktop/rsv_disruption/output/data/women/women_rate_prefitting_mobility.rds") %>%
                    filter(time <= 12*70, time > 12*60) %>%
                    ggplot() +
                    geom_bar(aes(x = time, y = proportion, fill = infection), position = "fill", stat = "identity") +
                    scale_fill_manual(values = c("lightgrey", "darkgrey", viridis(24))) +
                    scale_x_continuous(breaks = seq(1, 901, 6), labels = c(rep(c("January", "July"), 75), "January")) +
                    theme_bw() +
                    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                    labs(x = "Time",
                         y = "Proportion",
                         fill = "Infection Status"),
                  readRDS("/Users/lsh2301561/Desktop/rsv_disruption/output/data/women/women_rate_prefitting_scot.rds") %>%
                    filter(time <= 12*70, time > 12*60) %>%
                    ggplot() +
                    geom_bar(aes(x = time, y = proportion, fill = infection), position = "fill", stat = "identity") +
                    scale_fill_manual(values = c("lightgrey", "darkgrey", viridis(24))) +
                    scale_x_continuous(breaks = seq(1, 901, 6), labels = c(rep(c("January", "July"), 75), "January")) +
                    theme_bw() +
                    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                    labs(x = "Time",
                         y = "Proportion",
                         fill = "Infection Status"),
                  labels = c("original", "mobility", "scotland"),
                  nrow = 1)
```

```{r women_prop_shape, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot infection history proportions
readRDS("/Users/lsh2301561/Desktop/rsv_disruption/output/data/women/women_rate_prefitting_scot.rds") %>%
  filter(time <= 12*70, time > 12*60) %>%
  ggplot() +
  geom_bar(aes(x = time, y = proportion, fill = infection), position = "fill", stat = "identity") +
  scale_fill_manual(values = c("lightgrey", "darkgrey", viridis(24))) +
  scale_x_continuous(breaks = seq(1, 901, 6), labels = c(rep(c("January", "July"), 75), "January")) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Time",
       y = "Proportion",
       fill = "Infection Status")
```

**immunity split in babies**
```{r immunity_split_rate, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot immunity split
ggpubr::ggarrange(readRDS("/Users/lsh2301561/Desktop/rsv_disruption/output/data/women/women_rate_prefitting.rds") %>% 
                  filter(time <= 12*70, time > 12*60) %>% 
                  mutate(month = factor(month, levels = month.abb)) %>% 
                  filter(infection != "susceptible_naive") %>% 
                  mutate(level = as.factor(case_when(infection %in% str_c(rep("I", 6), 1:6) ~ 1,
                                                     infection %in% str_c(rep("I", 9), 7:15) ~ 2,
                                                     infection %in% str_c(rep("I", 9), 16:24) ~ 3,
                                                     infection == "susceptible_reinf" ~ 4))) %>% 
                  group_by(time, rate, month, level) %>% 
                  summarise(across(c("count", "proportion"), sum, na.rm = TRUE)) %>% 
                  ungroup() %>% 
                  mutate(time = rep(1:(12*10), each = 4)) %>% 
                  # combining with birth data
                  select(-count) %>% 
                  left_join(birth_data %>% select(month, births, time)) %>% 
                  mutate(susceptible = proportion * births) %>%
                  mutate(level = factor(level, levels = c("1", "2", "3", "4", "total"), labels = c("1 (high)", "2", "3", "4 (low)", "total"))) %>% 
                  ggplot() +
                  geom_bar(aes(x = time, y = proportion, fill = level), position = "fill", stat = "identity") +
                  geom_vline(xintercept = c(12*5+3, 12*6+3), linetype = "dashed", color = "red") +
                  scale_fill_manual(values = viridis(4)) +
                  scale_x_continuous(breaks = seq(1, 120, 3), 
                                     labels = rep(c("Jan", "Apr", "Jul", "Oct"), 10)) +
                  theme_bw() +
                  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                  labs(x = "Calendar Month",
                       y = "Proportion",
                       fill = "Immunity Level"),
                  readRDS("/Users/lsh2301561/Desktop/rsv_disruption/output/data/women/women_rate_prefitting_mobility.rds") %>% 
                  filter(time <= 12*70, time > 12*60) %>% 
                  mutate(month = factor(month, levels = month.abb)) %>% 
                  filter(infection != "susceptible_naive") %>% 
                  mutate(level = as.factor(case_when(infection %in% str_c(rep("I", 6), 1:6) ~ 1,
                                                     infection %in% str_c(rep("I", 9), 7:15) ~ 2,
                                                     infection %in% str_c(rep("I", 9), 16:24) ~ 3,
                                                     infection == "susceptible_reinf" ~ 4))) %>% 
                  group_by(time, rate, month, level) %>% 
                  summarise(across(c("count", "proportion"), sum, na.rm = TRUE)) %>% 
                  ungroup() %>% 
                  mutate(time = rep(1:(12*10), each = 4)) %>% 
                  # combining with birth data
                  select(-count) %>% 
                  left_join(birth_data %>% select(month, births, time)) %>% 
                  mutate(susceptible = proportion * births) %>%
                  mutate(level = factor(level, levels = c("1", "2", "3", "4", "total"), labels = c("1 (high)", "2", "3", "4 (low)", "total"))) %>% 
                  ggplot() +
                  geom_bar(aes(x = time, y = proportion, fill = level), position = "fill", stat = "identity") +
                  geom_vline(xintercept = c(12*5+3, 12*6+3), linetype = "dashed", color = "red") +
                  scale_fill_manual(values = viridis(4)) +
                  scale_x_continuous(breaks = seq(1, 120, 3), 
                                     labels = rep(c("Jan", "Apr", "Jul", "Oct"), 10)) +
                  theme_bw() +
                  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                  labs(x = "Calendar Month",
                       y = "Proportion",
                       fill = "Immunity Level"),
                  readRDS("/Users/lsh2301561/Desktop/rsv_disruption/output/data/women/women_rate_prefitting_scot.rds") %>% 
                  filter(time <= 12*70, time > 12*60) %>% 
                  mutate(month = factor(month, levels = month.abb)) %>% 
                  filter(infection != "susceptible_naive") %>% 
                  mutate(level = as.factor(case_when(infection %in% str_c(rep("I", 6), 1:6) ~ 1,
                                                     infection %in% str_c(rep("I", 9), 7:15) ~ 2,
                                                     infection %in% str_c(rep("I", 9), 16:24) ~ 3,
                                                     infection == "susceptible_reinf" ~ 4))) %>% 
                  group_by(time, rate, month, level) %>% 
                  summarise(across(c("count", "proportion"), sum, na.rm = TRUE)) %>% 
                  ungroup() %>% 
                  mutate(time = rep(1:(12*10), each = 4)) %>% 
                  # combining with birth data
                  select(-count) %>% 
                  left_join(birth_data %>% select(month, births, time)) %>% 
                  mutate(susceptible = proportion * births) %>%
                  mutate(level = factor(level, levels = c("1", "2", "3", "4", "total"), labels = c("1 (high)", "2", "3", "4 (low)", "total"))) %>% 
                  ggplot() +
                  geom_bar(aes(x = time, y = proportion, fill = level), position = "fill", stat = "identity") +
                  geom_vline(xintercept = c(12*5+3, 12*6+3), linetype = "dashed", color = "red") +
                  scale_fill_manual(values = viridis(4)) +
                  scale_x_continuous(breaks = seq(1, 120, 3), 
                                     labels = rep(c("Jan", "Apr", "Jul", "Oct"), 10)) +
                  theme_bw() +
                  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                  labs(x = "Calendar Month",
                       y = "Proportion",
                       fill = "Immunity Level"),
                  labels = c("original", "mobility", "scotland"),
                  nrow = 1)
```

```{r immunity_split_shape, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot immunity split
immunity_split %>%
  mutate(level = factor(level, levels = c("1", "2", "3", "4", "total"), labels = c("1 (high)", "2", "3", "4 (low)", "total"))) %>% 
  ggplot() +
  geom_bar(aes(x = time, y = proportion, fill = level), position = "fill", stat = "identity") +
  geom_vline(xintercept = c(12*5+3, 12*6+3), linetype = "dashed", color = "red") +
  scale_fill_manual(values = viridis(4)) +
  scale_x_continuous(breaks = seq(1, 120, 3), 
                     labels = rep(c("Jan", "Apr", "Jul", "Oct"), 10)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Calendar Month",
       y = "Proportion",
       fill = "Immunity Level")
```

# Mobility

**changes in mobility**
```{r mobility, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot changes in mobility
mobility %>% 
plot_ly(x = ~Day, 
        y = ~value, 
        split = ~category,
        group = ~category,
        colour = ~category,
        type = 'scatter', 
        mode = 'lines') %>%
  layout(xaxis = list(title = 'Date',
                      range = c(as.numeric(as.POSIXct("2018-01-01", format="%Y-%m-%d"))*1000,
                                as.numeric(as.POSIXct("2024-12-31", format="%Y-%m-%d"))*1000),
                      type = "date"),
         yaxis = list(title = 'Percent Change'),
         legend = list(orientation = "h",
                       xanchor = "center",
                       x = 0.5))
```

# Infection

**monthly first infection**
```{r inf, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
manipulateWidget::combineWidgets(plot_curve(one, max = 20000, tick = 2000, ind = "infected"),
                                 plot_curve(two, max = 20000, tick = 2000, ind = "infected"),
                                 plot_curve(three, max = 20000, tick = 2000, ind = "infected"),
                                 nrow = 1)
```

**monthly first infection by immunity level (sub-analysis of above)**
```{r inf_immunity, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot infection epidemic curve over time by immunity level
manipulateWidget::combineWidgets(plot_split(one, max = 20000, tick = 2000, ind = "infected"),
                                 plot_split(two, max = 20000, tick = 2000, ind = "infected"),
                                 plot_split(three, max = 20000, tick = 2000, ind = "infected"),
                                 nrow = 1,
                                 title = "Infection Count")
```

**proportion of age groups contributing to monthly cases of infection**
```{r inf_age, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot age distribution of infection over time
manipulateWidget::combineWidgets(plot_bar(one, ind = "infected"),
                                 plot_bar(two, ind = "infected"),
                                 plot_bar(three, ind = "infected"),
                                 nrow = 1)
```

**infection rate**
```{r inf_rate, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot infection rate per 100,000
manipulateWidget::combineWidgets(plot_rate(one, max = 16000, tick = 2000, ind = "infected"),
                                 plot_rate(two, max = 16000, tick = 2000, ind = "infected"),
                                 plot_rate(three, max = 16000, tick = 2000, ind = "infected"),
                                 nrow = 1)
```

# Disease

**monthly first occurrence of disease**
```{r dis, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot disease epidemic curve over time
manipulateWidget::combineWidgets(plot_curve(one, max = 6000, tick = 1000, ind = "disease"),
                                 plot_curve(two, max = 6000, tick = 1000, ind = "disease"),
                                 plot_curve(three, max = 6000, tick = 1000, ind = "disease"),
                                 nrow = 1)
```

**monthly first occurrence of disease by immunity level (sub-analysis of above)**
```{r dis_immunity, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot disease epidemic curve over time by immunity level
manipulateWidget::combineWidgets(plot_split(one, max = 10000, tick = 1000, ind = "disease"),
                                 plot_split(two, max = 10000, tick = 1000, ind = "disease"),
                                 plot_split(three, max = 10000, tick = 1000, ind = "disease"),
                                 nrow = 1)
```

**proportion of age groups contributing to monthly cases of disease**
```{r dis_age, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot age distribution of disease over time
manipulateWidget::combineWidgets(plot_bar(one, ind = "disease"),
                                 plot_bar(two, ind = "disease"),
                                 plot_bar(three, ind = "disease"),
                                 nrow = 1)
```

**disease rate**
```{r dis_rate, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot disease rate per 100,000
manipulateWidget::combineWidgets(plot_rate(one, max = 10000, tick = 2000, ind = "disease"),
                                 plot_rate(two, max = 10000, tick = 2000, ind = "disease"),
                                 plot_rate(three, max = 10000, tick = 2000, ind = "disease"),
                                 nrow = 1)
```