---
title: "Model Update"
output: html_document
date: "2024-04-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyr)
library(ggplot2)
library(plotly)
library(knitr)
library(viridisLite)
library(readxl)
library(zoo)
library(stringr)

```

```{r data, include=FALSE}
# load main data frame to be used
output <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/continuous_model.rds")

# load other datasets
# load birth data
birth_data <- read_excel("/Users/lsh2301561/Desktop/rsv_disruption/data/births_pregnancies.xlsx", sheet = "All") %>%
  mutate(year_month = paste(year, month, sep = "_"),
         date = as.Date(as.yearmon(`year_month`, "%Y_%b")),) %>%
  select(year, month, date, births) %>% 
  filter(!is.na(births)) %>% 
  slice(1:(12*10)) %>% 
  mutate(time = 1:nrow(.))

# create reference table for rates to join
rate_reference <- readRDS("/Users/lsh2301561/Desktop/rsv_disruption/output/data/women/women_long_disrupt.rds") %>% 
  select(time, month, rate) %>% 
  distinct() %>% 
  filter(time <= 12*75, time > 12*60) %>% 
  mutate(month = factor(month, levels = month.abb),
         time = 1:nrow(.)) %>% 
  cross_join(data.frame(level = 1:4)) %>% 
  mutate(level = factor(level, levels = 1:4))

# create 10 years of infection history/immunity split
immunity_split <- readRDS("/Users/lsh2301561/Desktop/rsv_disruption/output/data/women/women_long_disrupt.rds") %>% 
  filter(time <= 12*70, time > 12*60) %>% 
  mutate(month = factor(month, levels = month.abb)) %>% 
  filter(infection != "susceptible_naive") %>% 
  mutate(level = as.factor(case_when(infection %in% str_c(rep("I", 6), 1:6) ~ 1,
                                     infection %in% str_c(rep("I", 9), 7:15) ~ 2,
                                     infection %in% str_c(rep("I", 9), 16:24) ~ 3,
                                     infection == "susceptible_reinf" ~ 4))) %>% 
  group_by(time, rate, month, level) %>% 
  summarise(across(c("count", "proportion"), sum, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(time = rep(1:(12*10), each = 4)) %>% 
  # combining with birth data
  select(-count) %>% 
  left_join(birth_data %>% select(month, births, time)) %>% 
  mutate(susceptible = proportion * births)

```

# Immunity

**infection history in mothers**
```{r women_prop, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot infection history proportions
readRDS("/Users/lsh2301561/Desktop/rsv_disruption/output/data/women/women_long_disrupt.rds") %>%
  filter(time <= 12*70, time > 12*60) %>%
  ggplot() +
  geom_bar(aes(x = time, y = proportion, fill = infection), position = "fill", stat = "identity") +
  scale_fill_manual(values = c("lightgrey", "darkgrey", viridis(24))) +
  scale_x_continuous(breaks = seq(1, 901, 6), labels = c(rep(c("January", "July"), 75), "January")) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Time",
       y = "Proportion",
       fill = "Infection Status")
```

**immunity split in babies**
```{r immunity_split, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot immunity split
immunity_split %>%
  mutate(level = factor(level, levels = c("1", "2", "3", "4", "total"), labels = c("1 (high)", "2", "3", "4 (low)", "total"))) %>% 
  ggplot() +
  geom_bar(aes(x = time, y = proportion, fill = level), position = "fill", stat = "identity") +
  geom_vline(xintercept = c(12*5+3, 12*6+3), linetype = "dashed", color = "red") +
  scale_fill_manual(values = viridis(4)) +
  scale_x_continuous(breaks = seq(1, 120, 3), 
                     labels = rep(c("Jan", "Apr", "Jul", "Oct"), 10)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Calendar Month",
       y = "Proportion",
       fill = "Immunity Level")
```

# Infection

**monthly first infection**
```{r inf, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
output %>% 
  group_by(time_calendar, month, rate) %>% 
  summarise(across(c("susceptible", "infected", "disease"), sum, na.rm = TRUE)) %>% 
  ungroup() %>% 
  plot_ly() %>% 
  add_trace(
    x = ~time_calendar,
    y = ~infected,
    type = "scatter",
    mode = "line",
    text = ~month
  ) %>% 
  layout(xaxis = list(title = "Calendar month",
                      range = list(37, 120),
                      tickvals = seq(37, 120, 3),
                      ticktext = rep(c("Jan", "Apr", "Jul", "Oct"), 7),
                      tickmode = "array",
                      tickangle = -45),
         yaxis = list(title = "Infection Count",
                      range = list(0, 320000),
                      tickmode = "linear",
                      tick0 = 0,
                      dtick = 20000, 
                      tickformat = "digits"),
         shapes = list(list(type = "line",
                            y0 = 0,
                            y1 = 1,
                            yref = "paper",
                            x0 = 12*5+3,
                            x1 = 12*5+3,
                            line = list(color = "red", dash="dot")),
                       list(type = "line",
                            y0 = 0,
                            y1 = 1,
                            yref = "paper",
                            x0 = 12*6+3,
                            x1 = 12*6+3,
                            line = list(color = "red", dash="dot"))))
```

**monthly first infection by immunity level (sub-analysis of above)**
```{r inf_immunity, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot infection epidemic curve over time by immunity level
output %>% 
  group_by(time_calendar, month, rate, level) %>% 
  summarise(across(c("susceptible", "infected", "disease"), sum, na.rm = TRUE)) %>% 
  ungroup() %>% 
  plot_ly() %>% 
  add_trace(
    x = ~time_calendar,
    y = ~infected,
    type = "scatter",
    mode = "line",
    split = ~level,
    color = ~level, 
    colors = c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728"),
    text = ~month,
    hovertemplate = paste('<b>Month</b>: %{text}',
                          '<br><b>Count</b>: %{y}',
                          '<extra></extra>')
  ) %>% 
  layout(xaxis = list(title = "Calendar month",
                      range = list(37, 120),
                      tickvals = seq(37, 120, 3),
                      ticktext = rep(c("Jan", "Apr", "Jul", "Oct"), 7),
                      tickmode = "array",
                      tickangle = -45),
         yaxis = list(title = "Infection Count",
                      range = list(0, 180000),
                      tickmode = "linear",
                      tick0 = 0,
                      dtick = 10000, 
                      tickformat = "digits"),
         legend = list(title = list(text = "Immunity Level")),
         shapes = list(list(type = "line",
                            y0 = 0,
                            y1 = 1,
                            yref = "paper",
                            x0 = 12*5+3,
                            x1 = 12*5+3,
                            line = list(color = "red", dash="dot")),
                       list(type = "line",
                            y0 = 0,
                            y1 = 1,
                            yref = "paper",
                            x0 = 12*6+3,
                            x1 = 12*6+3,
                            line = list(color = "red", dash="dot"))))
```

**proportion of age groups contributing to monthly cases of infection**
```{r inf_age, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot age distribution of infection over time
output %>% 
  select(-time) %>% 
  pivot_longer(cols = c("<6", "6-12", "12-24", "24-36"), names_to = "age", values_to = "value") %>%
  mutate(age = factor(age, levels = c("<6", "6-12", "12-24", "24-36"))) %>% 
  filter(value == 1) %>% 
  select(-value) %>% 
  group_by(time_calendar, month, rate, age) %>% 
  summarise(infected = sum(infected),
            disease = sum(disease)) %>% 
  ungroup() %>% 
  pivot_longer(cols = c("infected", "disease"), names_to = "type", values_to = "count") %>% 
  left_join(output %>%
            group_by(time_calendar, month, rate) %>%
            summarise(across(c("infected", "disease"), sum, na.rm = TRUE)) %>%
            ungroup() %>%
            pivot_longer(cols = c("infected", "disease"), names_to = "type", values_to = "sum")) %>%
  mutate(proportion = (count/sum)*100) %>% 
  filter(type == "infected") %>% 
  plot_ly() %>%
  add_trace(x = ~time_calendar,
            y = ~proportion,
            split = ~age,
            color = ~age, 
            colors = c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728"),
            legendgroup = ~age,
            type = "bar",
            showlegend = TRUE) %>% 
  layout(xaxis = list(title = "Calendar Month",
                      range = list(37, 120),
                      tickvals = seq(37, 120, 3),
                      ticktext = rep(c("Jan", "Apr", "Jul", "Oct"), 7),
                      tickmode = "array",
                      tickangle = -45),
         yaxis = list(title = "Proportion"),
         legend = list(title = list(text = "Age Group")),
         barmode = "stack",
         shapes = list(list(type = "line",
                            y0 = 0,
                            y1 = 1,
                            yref = "paper",
                            x0 = 12*5+3,
                            x1 = 12*5+3,
                            line = list(color = "red", dash="dot")),
                       list(type = "line",
                            y0 = 0,
                            y1 = 1,
                            yref = "paper",
                            x0 = 12*6+3,
                            x1 = 12*6+3,
                            line = list(color = "red", dash="dot"))))
```

# Disease

**monthly first occurrence of disease**
```{r dis, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot disease epidemic curve over time
output %>%
  group_by(time_calendar, month, rate) %>%
  summarise(across(c("susceptible", "infected", "disease"), sum, na.rm = TRUE)) %>%
  ungroup() %>%
  plot_ly() %>%
  add_trace(
    x = ~time_calendar,
    y = ~disease,
    type = "scatter",
    mode = "line",
    text = ~month
  ) %>%
  layout(xaxis = list(title = "Calendar month",
                      range = list(37, 120),
                      tickvals = seq(37, 120, 3),
                      ticktext = rep(c("Jan", "Apr", "Jul", "Oct"), 7),
                      tickmode = "array",
                      tickangle = -45),
         yaxis = list(title = "Infection Count",
                      range = list(0, 100000),
                      tickmode = "linear",
                      tick0 = 0,
                      dtick = 5000,
                      tickformat = "digits"),
         shapes = list(list(type = "line",
                            y0 = 0,
                            y1 = 1,
                            yref = "paper",
                            x0 = 12*5+3,
                            x1 = 12*5+3,
                            line = list(color = "red", dash="dot")),
                       list(type = "line",
                            y0 = 0,
                            y1 = 1,
                            yref = "paper",
                            x0 = 12*6+3,
                            x1 = 12*6+3,
                            line = list(color = "red", dash="dot"))))
```

**monthly first occurrence of disease by immunity level (sub-analysis of above)**
```{r dis_immunity, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot disease epidemic curve over time by immunity level
output %>%
  group_by(time_calendar, month, rate, level) %>%
  summarise(across(c("susceptible", "infected", "disease"), sum, na.rm = TRUE)) %>%
  ungroup() %>%
  plot_ly() %>%
  add_trace(
    x = ~time_calendar,
    y = ~disease,
    type = "scatter",
    mode = "line",
    split = ~level,
    color = ~level,
    colors = c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728"),
    text = ~month,
    hovertemplate = paste('<b>Month</b>: %{text}',
                          '<br><b>Count</b>: %{y}',
                          '<extra></extra>')
  ) %>%
  layout(xaxis = list(title = "Calendar month",
                      range = list(37, 120),
                      tickvals = seq(37, 120, 3),
                      ticktext = rep(c("Jan", "Apr", "Jul", "Oct"), 7),
                      tickmode = "array",
                      tickangle = -45),
         yaxis = list(title = "Infection Count",
                      range = list(0, 80000),
                      tickmode = "linear",
                      tick0 = 0,
                      dtick = 5000,
                      tickformat = "digits"),
         legend = list(title = list(text = "Immunity Level")),
         shapes = list(list(type = "line",
                            y0 = 0,
                            y1 = 1,
                            yref = "paper",
                            x0 = 12*5+3,
                            x1 = 12*5+3,
                            line = list(color = "red", dash="dot")),
                       list(type = "line",
                            y0 = 0,
                            y1 = 1,
                            yref = "paper",
                            x0 = 12*6+3,
                            x1 = 12*6+3,
                            line = list(color = "red", dash="dot"))))
```

**proportion of age groups contributing to monthly cases of disease**
```{r dis_age, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
# plot age distribution of disease over time
output %>%
  select(-time) %>%
  pivot_longer(cols = c("<6", "6-12", "12-24", "24-36"), names_to = "age", values_to = "value") %>%
  mutate(age = factor(age, levels = c("<6", "6-12", "12-24", "24-36"))) %>%
  filter(value == 1) %>%
  select(-value) %>%
  group_by(time_calendar, month, rate, age) %>%
  summarise(infected = sum(infected),
            disease = sum(disease)) %>%
  ungroup() %>%
  pivot_longer(cols = c("infected", "disease"), names_to = "type", values_to = "count") %>%
  left_join(output %>%
              group_by(time_calendar, month, rate) %>%
              summarise(across(c("infected", "disease"), sum, na.rm = TRUE)) %>%
              ungroup() %>%
              pivot_longer(cols = c("infected", "disease"), names_to = "type", values_to = "sum")) %>%
  mutate(proportion = (count/sum)*100) %>%
  filter(type == "disease") %>%
  plot_ly() %>%
  add_trace(x = ~time_calendar,
            y = ~proportion,
            split = ~age,
            color = ~age,
            colors = c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728"),
            legendgroup = ~age,
            type = "bar",
            showlegend = TRUE) %>%
  layout(xaxis = list(title = "Calendar Month",
                      range = list(37, 120),
                      tickvals = seq(37, 120, 3),
                      ticktext = rep(c("Jan", "Apr", "Jul", "Oct"), 7),
                      tickmode = "array",
                      tickangle = -45),
         yaxis = list(title = "Proportion"),
         legend = list(title = list(text = "Age Group")),
         barmode = "stack",
         shapes = list(list(type = "line",
                            y0 = 0,
                            y1 = 1,
                            yref = "paper",
                            x0 = 12*5+3,
                            x1 = 12*5+3,
                            line = list(color = "red", dash="dot")),
                       list(type = "line",
                            y0 = 0,
                            y1 = 1,
                            yref = "paper",
                            x0 = 12*6+3,
                            x1 = 12*6+3,
                            line = list(color = "red", dash="dot"))))

```