---
title: "Infection and Disease by Month of Birth"
output: html_document
date: "2024-03-14"
---

<style type="text/css">
  body{
  font-size: 14pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyr)
library(ggplot2)
library(plotly)
library(knitr)

source(file = "/Users/lsh2301561/Desktop/rsv_disruption/code/plot/plot_births.R")
```

```{r data, include=FALSE}
women_prop <- readRDS("/Users/lsh2301561/Desktop/rsv_disruption/output/data/women/women_prop.rds")

births_year <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/disruption/births_year.rds")
births_age <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/disruption/births_age.rds")
births_age_month <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/disruption/births_age_month.rds")

births_year_disrupt <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/disruption/births_year_disrupt.rds")
births_age_disrupt <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/disruption/births_age_disrupt.rds")
births_age_month_disrupt <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/disruption/births_age_month_disrupt.rds")

```

# Immunity level split
```{r immunity, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
immunity <- women_prop %>%
  mutate(disruption = factor(disruption, levels = 0:3, labels = c("No disruption", "Beginning of disruption", "1 year after disruption", "2 years after disruption")),
         level = factor(level, levels = c("1", "2", "3", "4", "total"), labels = c("1 (high)", "2", "3", "4 (low)", "total"))) %>% 
  ggplot() +
  geom_bar(aes(x = month, y = proportion, fill = level), position = "fill", stat = "identity") +
  scale_fill_manual(values = viridis(4)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Month",
       y = "Proportion",
       fill = "Immunity Level") + 
  facet_wrap(~disruption, nrow = 2, ncol = 2)

immunity
```

# Infections

**First infection by month of birth**
<br/> <font size="3">No disruption</font>
```{r inf, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
inf <- subplot(
  plot_infections(births_year %>% filter(month_born == "Jan")),
  plot_infections(births_year %>% filter(month_born == "Feb")),
  plot_infections(births_year %>% filter(month_born == "Mar")),
  plot_infections(births_year %>% filter(month_born == "Apr")),
  plot_infections(births_year %>% filter(month_born == "May")),
  plot_infections(births_year %>% filter(month_born == "Jun")),
  plot_infections(births_year %>% filter(month_born == "Jul")),
  plot_infections(births_year %>% filter(month_born == "Aug")),
  plot_infections(births_year %>% filter(month_born == "Sep")),
  plot_infections(births_year %>% filter(month_born == "Oct")),
  plot_infections(births_year %>% filter(month_born == "Nov")),
  plot_infections(births_year %>% filter(month_born == "Dec")),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.05, 0.06)
)

for(n in 6:60){
  inf[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

inf
```
<font size="3">Beginning of disruption</font>
```{r inf_1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
inf_1 <- subplot(
  plot_infections(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Jan")),
  plot_infections(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Feb")),
  plot_infections(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Mar")),
  plot_infections(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Apr")),
  plot_infections(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "May")),
  plot_infections(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Jun")),
  plot_infections(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Jul")),
  plot_infections(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Aug")),
  plot_infections(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Sep")),
  plot_infections(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Oct")),
  plot_infections(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Nov")),
  plot_infections(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Dec")),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.05, 0.06)
)

for(n in 6:60){
  inf_1[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

inf_1
```
<font size="3">1 year after disruption</font>
```{r inf_2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
inf_2 <- subplot(
  plot_infections(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Jan")),
  plot_infections(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Feb")),
  plot_infections(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Mar")),
  plot_infections(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Apr")),
  plot_infections(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "May")),
  plot_infections(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Jun")),
  plot_infections(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Jul")),
  plot_infections(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Aug")),
  plot_infections(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Sep")),
  plot_infections(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Oct")),
  plot_infections(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Nov")),
  plot_infections(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Dec")),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.05, 0.06)
)

for(n in 6:60){
  inf_2[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

inf_2
```
<font size="3">2 years after disruption</font>
```{r inf_3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
inf_3 <- subplot(
  plot_infections(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Jan")),
  plot_infections(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Feb")),
  plot_infections(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Mar")),
  plot_infections(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Apr")),
  plot_infections(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "May")),
  plot_infections(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Jun")),
  plot_infections(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Jul")),
  plot_infections(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Aug")),
  plot_infections(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Sep")),
  plot_infections(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Oct")),
  plot_infections(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Nov")),
  plot_infections(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Dec")),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.05, 0.06)
)

for(n in 6:60){
  inf_3[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

inf_3
```

**Cumulative first infection by month of birth**
<br/> <font size="3">No disruption</font>
```{r cum_inf, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
cum_inf <- subplot(plot_cumpropinf(births_year),
                   plot_cumprop(births_age_month, type = "infection"),
                   nrows = 1,
                   shareX = FALSE,
                   shareY = FALSE)

for(n in 13:24){
  cum_inf[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

cum_inf
```
<font size="3">Beginning of disruption</font>
```{r cum_inf_1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
cum_inf_1 <- subplot(plot_cumpropinf(births_year_disrupt %>% filter(disruption == 1)),
                     plot_cumprop(births_age_month_disrupt %>% filter(disruption == 1), type = "infection"),
                     nrows = 1,
                     shareX = FALSE,
                     shareY = FALSE)

for(n in 13:24){
  cum_inf_1[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

cum_inf_1
```
<font size="3">1 year after disruption</font>
```{r cum_inf_2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
cum_inf_2 <- subplot(plot_cumpropinf(births_year_disrupt %>% filter(disruption == 2)),
                     plot_cumprop(births_age_month_disrupt %>% filter(disruption == 2), type = "infection"),
                     nrows = 1,
                     shareX = FALSE,
                     shareY = FALSE)

for(n in 13:24){
  cum_inf_2[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

cum_inf_2
```
<font size="3">2 years after disruption</font>
```{r cum_inf_3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
cum_inf_3 <- subplot(plot_cumpropinf(births_year_disrupt %>% filter(disruption == 3)),
                     plot_cumprop(births_age_month_disrupt %>% filter(disruption == 3), type = "infection"),
                     nrows = 1,
                     shareX = FALSE,
                     shareY = FALSE)

for(n in 13:24){
  cum_inf_3[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

cum_inf_3
```

**Age at first infection by month of birth**
<br/> <font size="3">No disruption</font>
```{r age_inf, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
age_inf <- subplot(
  plot_age(births_age %>% filter(month_born == "Jan"), types = "infected"),
  plot_age(births_age %>% filter(month_born == "Feb"), types = "infected"),
  plot_age(births_age %>% filter(month_born == "Mar"), types = "infected"),
  plot_age(births_age %>% filter(month_born == "Apr"), types = "infected"),
  plot_age(births_age %>% filter(month_born == "May"), types = "infected"),
  plot_age(births_age %>% filter(month_born == "Jun"), types = "infected"),
  plot_age(births_age %>% filter(month_born == "Jul"), types = "infected"),
  plot_age(births_age %>% filter(month_born == "Aug"), types = "infected"),
  plot_age(births_age %>% filter(month_born == "Sep"), types = "infected"),
  plot_age(births_age %>% filter(month_born == "Oct"), types = "infected"),
  plot_age(births_age %>% filter(month_born == "Nov"), types = "infected"),
  plot_age(births_age %>% filter(month_born == "Dec"), types = "infected"),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.03, 0.05)
)

for(n in 6:60){
  age_inf[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

age_inf
```
<font size="3">Beginning of disruption</font>
```{r age_inf_1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
age_inf_1 <- subplot(
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Jan"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Feb"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Mar"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Apr"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "May"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Jun"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Jul"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Aug"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Sep"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Oct"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Nov"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Dec"), types = "infected"),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.03, 0.05)
)

for(n in 6:60){
  age_inf_1[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

age_inf_1
```
<font size="3">1 year after disruption</font>
```{r age_inf_2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
age_inf_2 <- subplot(
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Jan"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Feb"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Mar"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Apr"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "May"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Jun"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Jul"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Aug"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Sep"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Oct"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Nov"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Dec"), types = "infected"),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.03, 0.05)
)

for(n in 6:60){
  age_inf_2[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

age_inf_2
```
<font size="3">2 years after disruption</font>
```{r age_inf_3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
age_inf_3 <- subplot(
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Jan"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Feb"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Mar"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Apr"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "May"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Jun"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Jul"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Aug"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Sep"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Oct"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Nov"), types = "infected"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Dec"), types = "infected"),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.03, 0.05)
)

for(n in 6:60){
  age_inf_3[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

age_inf_3
```

## Disease

**First occurence of disease by month of birth**
<br/> <font size="3">No disruption</font>
```{r dis, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
dis <- subplot(
  plot_disease(births_year %>% filter(month_born == "Jan")),
  plot_disease(births_year %>% filter(month_born == "Feb")),
  plot_disease(births_year %>% filter(month_born == "Mar")),
  plot_disease(births_year %>% filter(month_born == "Apr")),
  plot_disease(births_year %>% filter(month_born == "May")),
  plot_disease(births_year %>% filter(month_born == "Jun")),
  plot_disease(births_year %>% filter(month_born == "Jul")),
  plot_disease(births_year %>% filter(month_born == "Aug")),
  plot_disease(births_year %>% filter(month_born == "Sep")),
  plot_disease(births_year %>% filter(month_born == "Oct")),
  plot_disease(births_year %>% filter(month_born == "Nov")),
  plot_disease(births_year %>% filter(month_born == "Dec")),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.05, 0.06)
)

for(n in 6:60){
  dis[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

dis
```
<font size="3">Beginning of disruption</font>
```{r dis_1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
dis_1 <- subplot(
  plot_disease(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Jan")),
  plot_disease(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Feb")),
  plot_disease(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Mar")),
  plot_disease(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Apr")),
  plot_disease(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "May")),
  plot_disease(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Jun")),
  plot_disease(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Jul")),
  plot_disease(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Aug")),
  plot_disease(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Sep")),
  plot_disease(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Oct")),
  plot_disease(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Nov")),
  plot_disease(births_year_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Dec")),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.05, 0.06)
)

for(n in 6:60){
  dis_1[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

dis_1
```
<font size="3">1 year after disruption</font>
```{r dis_2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
dis_2 <- subplot(
  plot_disease(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Jan")),
  plot_disease(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Feb")),
  plot_disease(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Mar")),
  plot_disease(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Apr")),
  plot_disease(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "May")),
  plot_disease(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Jun")),
  plot_disease(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Jul")),
  plot_disease(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Aug")),
  plot_disease(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Sep")),
  plot_disease(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Oct")),
  plot_disease(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Nov")),
  plot_disease(births_year_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Dec")),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.05, 0.06)
)

for(n in 6:60){
  dis_2[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

dis_2
```
<font size="3">2 years after disruption</font>
```{r dis_3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
dis_3 <- subplot(
  plot_disease(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Jan")),
  plot_disease(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Feb")),
  plot_disease(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Mar")),
  plot_disease(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Apr")),
  plot_disease(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "May")),
  plot_disease(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Jun")),
  plot_disease(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Jul")),
  plot_disease(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Aug")),
  plot_disease(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Sep")),
  plot_disease(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Oct")),
  plot_disease(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Nov")),
  plot_disease(births_year_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Dec")),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.05, 0.06)
)

for(n in 6:60){
  dis_3[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

dis_3
```

**Cumulative first occurrence of disease by month of birth**
<br/> <font size="3">No disruption</font>
```{r cum_dis, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
cum_dis <- subplot(plot_cumpropdis(births_year),
                   plot_cumprop(births_age_month, type = "disease"),
                   nrows = 1,
                   shareX = FALSE,
                   shareY = FALSE)

for(n in 13:24){
  cum_dis[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

cum_dis
```
<font size="3">Beginning of disruption</font>
```{r cum_dis_1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
cum_dis_1 <- subplot(plot_cumpropdis(births_year_disrupt %>% filter(disruption == 1)),
                     plot_cumprop(births_age_month_disrupt %>% filter(disruption == 1), type = "disease"),
                     nrows = 1,
                     shareX = FALSE,
                     shareY = FALSE)

for(n in 13:24){
  cum_dis_1[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

cum_dis_1
```
<font size="3">1 year after disruption</font>
```{r cum_dis_2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
cum_dis_2 <- subplot(plot_cumpropdis(births_year_disrupt %>% filter(disruption == 2)),
                     plot_cumprop(births_age_month_disrupt %>% filter(disruption == 2), type = "disease"),
                     nrows = 1,
                     shareX = FALSE,
                     shareY = FALSE)

for(n in 13:24){
  cum_dis_2[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

cum_dis_2
```
<font size="3">2 years after disruption</font>
```{r cum_dis_3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
cum_dis_3 <- subplot(plot_cumpropdis(births_year_disrupt %>% filter(disruption == 3)),
                     plot_cumprop(births_age_month_disrupt %>% filter(disruption == 3), type = "disease"),
                     nrows = 1,
                     shareX = FALSE,
                     shareY = FALSE)

for(n in 13:24){
  cum_dis_3[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

cum_dis_3
```

**Age at first occurence of disease by month of birth**

<br/> <font size="3">No disruption</font>
```{r age_dis, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
age_dis <- subplot(
  plot_age(births_age %>% filter(month_born == "Jan"), types = "disease"),
  plot_age(births_age %>% filter(month_born == "Feb"), types = "disease"),
  plot_age(births_age %>% filter(month_born == "Mar"), types = "disease"),
  plot_age(births_age %>% filter(month_born == "Apr"), types = "disease"),
  plot_age(births_age %>% filter(month_born == "May"), types = "disease"),
  plot_age(births_age %>% filter(month_born == "Jun"), types = "disease"),
  plot_age(births_age %>% filter(month_born == "Jul"), types = "disease"),
  plot_age(births_age %>% filter(month_born == "Aug"), types = "disease"),
  plot_age(births_age %>% filter(month_born == "Sep"), types = "disease"),
  plot_age(births_age %>% filter(month_born == "Oct"), types = "disease"),
  plot_age(births_age %>% filter(month_born == "Nov"), types = "disease"),
  plot_age(births_age %>% filter(month_born == "Dec"), types = "disease"),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.03, 0.05)
)

for(n in 6:60){
  age_dis[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

age_dis
```
<font size="3">Beginning of disruption</font>
```{r age_dis_1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
age_dis_1 <- subplot(
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Jan"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Feb"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Mar"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Apr"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "May"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Jun"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Jul"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Aug"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Sep"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Oct"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Nov"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 1) %>% filter(month_born == "Dec"), types = "disease"),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.03, 0.05)
)

for(n in 6:60){
  age_dis_1[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

age_dis_1
```
<font size="3">1 year after disruption</font>
```{r age_dis_2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
age_dis_2 <- subplot(
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Jan"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Feb"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Mar"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Apr"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "May"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Jun"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Jul"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Aug"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Sep"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Oct"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Nov"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 2) %>% filter(month_born == "Dec"), types = "disease"),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.03, 0.05)
)

for(n in 6:60){
  age_dis_2[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

age_dis_2
```
<font size="3">2 years after disruption</font>
```{r age_dis_3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
age_dis_3 <- subplot(
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Jan"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Feb"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Mar"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Apr"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "May"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Jun"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Jul"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Aug"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Sep"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Oct"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Nov"), types = "disease"),
  plot_age(births_age_disrupt %>% filter(disruption == 3) %>% filter(month_born == "Dec"), types = "disease"),
  nrows = 4,
  shareX = FALSE,
  shareY = TRUE,
  margin = c(0.02, 0.02, 0.03, 0.05)
)

for(n in 6:60){
  age_dis_3[["x"]][["data"]][[n]][["showlegend"]] <-  FALSE
}

age_dis_3
```
