---
title: "Waning and Aging Comparison"
output: html_document
date: "2024-03-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyr)
library(plotly)

source(file = "/Users/lsh2301561/Desktop/rsv_disruption/code/plot/plot_births.R")
```

```{r data, include=FALSE}
births <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/births.rds")
births_waning <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/births_waning.rds")
births_aging <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/births_aging.rds")
births_waning_aging <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/births_waning_aging.rds")
women_prop <- readRDS(file = "/Users/lsh2301561/Desktop/rsv_disruption/output/data/women_prop.rds")
```
## Rate of Exposure

Rate of exposure remains unchanged by waning immunity and/or aging.

```{r rate, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
births %>% plot_rate()
```

## Probability of Infection

Probability of infection increases with time due to waning immunity.

```{r prob_inf, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
manipulateWidget::combineWidgets(births %>% plot_probability(type = "infection") %>% layout(title = "No Waning or Aging"),
                                 births_waning %>% plot_probability(type = "infection") %>% layout(title = "Waning"),
                                 births_aging %>% plot_probability(type = "infection") %>% layout(title = "Aging"),
                                 births_waning_aging %>% plot_probability(type = "infection") %>% layout(title = "Waning and Aging"),
                                 nrow = 2)
```

## Probability of Disease

Probability of disease decreases with time due to aging.

```{r prob_dis, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
manipulateWidget::combineWidgets(births %>% plot_probability(type = "disease") %>% layout(title = "No Waning or Aging"),
                                 births_waning %>% plot_probability(type = "disease") %>% layout(title = "Waning"),
                                 births_aging %>% plot_probability(type = "disease") %>% layout(title = "Aging"),
                                 births_waning_aging %>% plot_probability(type = "disease") %>% layout(title = "Waning and Aging"),
                                 nrow = 2)
```

## Immunity Level Split

Proportion of babies in immunity levels at birth.

```{r proportion, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
women_prop %>% 
  filter(month == "Jan") %>% 
  plot_ly() %>% 
  add_trace(x = ~month,
            y = ~proportion*100,
            type = "bar",
            color = ~level, 
            text = ~round(proportion*100, 2),
            hoverinfo = "text") %>% 
  layout(yaxis = list(title = "Percentage (%)"),
         barmode = "stack")
```

## Infection

Monthly count of first infections.

```{r infection, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
manipulateWidget::combineWidgets(births %>% plot_infections() %>% layout(title = "No Waning or Aging"),
                                 births_waning %>% plot_infections() %>% layout(title = "Waning"),
                                 births_aging %>% plot_infections() %>% layout(title = "Aging"),
                                 births_waning_aging %>% plot_infections() %>% layout(title = "Waning and Aging"),
                                 nrow = 2)
```

## Cumulative Infections

Cumulative first infection proportions.

```{r cumpropinf, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
manipulateWidget::combineWidgets(births %>% plot_cumpropinf() %>% layout(title = "No Waning or Aging"),
                                 births_waning %>% plot_cumpropinf() %>% layout(title = "Waning"),
                                 births_aging %>% plot_cumpropinf() %>% layout(title = "Aging"),
                                 births_waning_aging %>% plot_cumpropinf() %>% layout(title = "Waning and Aging"),
                                 nrow = 2)
```

## Disease

Monthly count of first occurrence of disease.

```{r disease, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
manipulateWidget::combineWidgets(births %>% plot_disease() %>% layout(title = "No Waning or Aging"),
                                 births_waning %>% plot_disease() %>% layout(title = "Waning"),
                                 births_aging %>% plot_disease() %>% layout(title = "Aging"),
                                 births_waning_aging %>% plot_disease() %>% layout(title = "Waning and Aging"),
                                 nrow = 2)
```

## Cumulative Disease

Cumulative proportions of babies experiencing disease for the first time.

```{r cumpropdis, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12}
manipulateWidget::combineWidgets(births %>% plot_cumpropdis() %>% layout(title = "No Waning or Aging"),
                                 births_waning %>% plot_cumpropdis() %>% layout(title = "Waning"),
                                 births_aging %>% plot_cumpropdis() %>% layout(title = "Aging"),
                                 births_waning_aging %>% plot_cumpropdis() %>% layout(title = "Waning and Aging"),
                                 nrow = 2)
```